Initial Analysis

### 2019-05-24 Initial_Analysis.Rmd
Small details

  # Get the index for testing
  Index_EEZ <- Neighbors %>% 
    select(INDEX)

  # Estimate total spp distribution within neighbours
  Trans_Spp <- SppDist %>%
    filter(INDEX %in% Index_EEZ$INDEX) %>% 
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
    filter(Model_Index > 0) %>% 
    mutate(Model_Index = Model_Index*100) %>% 
    left_join(Neighbors,
              by = "INDEX")

>>>>

  # Get the index for testing
  # Index_EEZ <- Neighbors %>% 
  #   select(INDEX)

  # Estimate total spp distribution within neighbours
  Trans_Spp <- SppDist %>%
    # filter(INDEX %in% Index_EEZ$INDEX) %>% # For testing
    mutate(Value = ifelse(Value > 0, 1,0)) %>%  # For now using SAU_C as presence absence
    group_by(TaxonKey,
             INDEX
    ) %>%
    summarise(Model_Index = mean(Value,na.rm=T)) %>% 
    filter(Model_Index > 0) %>% 
    mutate(Model_Index = Model_Index*100) %>% 
    left_join(Neighbors,
              by = "INDEX")
